When two-point correlation function fails to describe a structure...

### 2024-03-12 paper.tex
Kinda intro + abstract

\section{Introduction}
AAA BBB

>>>>

\begin{abstract}
  In this paper the two-point correlation function $S_2$ for arrays which
  elements are either 0 or 1 is studied and mechanisms of formation of
  collisions in $S_2$ are determined. A collision in $S_2$ is two different
  arrays which result in the same two-point correlation function. It is shown
  that there are only two trivial collisions obtained by simple transformations
  of the input array, when dimensions of the input array coincide with
  dimensions of its bounding box. It is also shown that some input arrays have
  non-trivial collisions which cannot be obtained by application of simple
  transformations. The algorithm for finding non-trivial collisions for any
  particular input array is shown in the paper and it is stated that the
  probability of finding non-trivial collision by randomly picking the input
  array tends to zero with increase in the input array's dimensions.
\end{abstract}

\section{Introduction}
In this paper we designate polynomials either $f$ or $f(x)$. The latter
designation is usually used when it's important to know the variable or to
differentiate a polynomial $f_k(x)$ from a coefficient $f_k$.
